Inequalities Witnessing Quantum Incompatibility in The Triangle Scenario

### 2016-10-31 document/main.tex
Use LOCAL version of kbordermatrix.sty, for ShareLatex compatibility.
Refined some notation for symmetries

% === To allow for labeling of rows and columns of a matrix ===
\usepackage{kbordermatrix}
\renewcommand{\kbldelim}{(} % Left delimiter
\renewcommand{\kbrdelim}{)} % Right delimiter

% === Commonly re-occurring symbols ===
\newcommand{\hgraph}{\mathcal{H}}
\newcommand{\graph}{\mathcal{G}}
\newcommand{\nodes}{\mathcal{N}}
\newcommand{\weights}{\mathcal{W}}
\newcommand{\edges}{\mathcal{E}}
\newcommand{\trans}{\mathcal{T}}
\newcommand{\ind}{S}
\newcommand{\inhibit}{\mathcal{I}}
\newcommand{\netperm}{\Pi}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ancestralindep}{\perp}
\newcommand{\valprod}{\times}
\newcommand{\bigvalprod}{\prod}
\newcommand{\com}{\mathrel{\Yright\hspace{-0.2em}\Yleft}}
\newcommand{\ext}{\mathrel{\Yleft}}
\newcommand{\res}{\mathrel{\Yright}}
\newcommand{\gep}{\varphi}
\newcommand{\gp}{\Phi}
\newcommand{\geo}{\omega}
\newcommand{\go}{\Omega}
\newcommand{\mscenario}{\mathcal{M}}
\newcommand{\jointvar}{\mathcal{J}}
\newcommand{\mset}{\gamma}
\newcommand{\extmset}{\Gamma}
\newcommand{\supp}[1]{\si\br{#1}}
\newcommand{\kone}{\mathbf{1}}
\newcommand{\kzer}{\textcolor{gray}{0}}

% \newcommand{\mext}[1]{E_{#1}}
% \newcommand{\mul}[1]{\Gamma_{#1}}
\newcommand{\isext}[2]{\delta_{#1 \ext #2}}
\newcommand{\ts}{{\graph}}
% When I introduce a new term or definition
\newcommand{\term}[1]{\textcolor{Mahogany}{\textbf{#1}}}

@@

\setoperator{Pa} % Parents of a node
\setoperator{Ch} % Children of a node
\setoperator{An} % Ancestry of a node
\setoperator{Sub} % subgraph
\setoperator{AnSub} % Ancestral subgraph
\setoperator{Ext} % Extension of outcomes
\setoperator{Com} % Compatible equivalence relation
\setoperator{Nec} % Necessary nodes
\setoperator{UnNec} % Unnecessary nodes
\setoperator{Inj} % injectable sets
\setoperator{ImInj} % images of the injectable sets
\setoperator{PreInj} % Pre-injectable sets
\setoperator{ImPreInj} % images of the Pre-injectable sets
\setoperator{Aut} % graph automorphism
\setoperator{Orb} % Group Orbits
\setoperator{Perm} % Permutation group
% \setoperator{Out} % Outcome space
\newcommand{\Sect}[1]{\s{S}\br{#1}} % Outcome space
\newcommand{\Dom}[1]{\s{D}\br{#1}} % Domian
% \setoperator{Dom} % Domian
% \setoperator{Dom} % Domian

@@

    \subsubsection{Sections}
    To every discrete random variable $v$ there corresponds a prescribed set of \term{outcomes} $O_v$. We also define the set of all \term{sections over $v$} $\Sect{v}$\footnote{Technically $\Sect{v}$ can be called a \textit{sheaf} but we neglect to introduce that terminology here.} to be the set of all functions $s : \bc{v} \to O_v$ each representing the event that a measurement on $v$ was made where $s\br{v} \in O_v$ was observed.
    \[ \Sect{v} \defined \bc{s : \bc{v} \to O_v} \label{eq:outcome_space} \]
    Making the unfamiliar distinction between sections $s$ and outcomes in $O_v$ might seem pedantic. Evidently, $\Sect{v}$ and $O_v$ have a one-to-one correspondence. There is rarely any harm in referring synonymously to either as outcomes. Nonetheless, a sheaf-theoretic treatment of contextuality~\cite{Abramsky_2011} demands the distinction.
    Specifically for this work, the distinction becomes essential for our discussion and exploit of marginal symmetries in \cref{sec:symmetry}. As a natural generalization we define the tuple sections for collection of random variables $V = \bc{v_1, \ldots, v_n}$ in a parallel manner,
    \[ \Sect{V} \defined \bc{s: V \to O_{V} \mid \forall i : s\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
    Each section $s$ can be compactly represented as a set of mappings over each element of $V$.
    \[ s = \bc{v_1 \mapsto s\br{v_1}, \ldots, v_k \mapsto s\br{v_k}} = \bc{v_i\mapsto s\br{v_i}}_{i = 1}^{k} \]
    The domain $\Dom{s}$ of an section $s$ is the set of random variables it valuates, i.e. if $s \in \Sect{V}$, then $\Dom{s} = V$.
    \begin{example}
        Let $s \in \Sect{V}$ be a section over $V$, a probability distribution $\prob[V]$ over $V$ will assign a non-negative probability $\prob[V][s]$ to $s$. Let $V = \bc{v_1, v_2}$ with each $v \in V$ having $3$ distinct outcomes $O_v = \bc{0,1,2}$. Furthermore let $f \in \Sect{V}$ be the section $\br{v_1 \mapsto 2, v_2 \mapsto 1}$. Then the following notations are interchangeable,
        \[ \prob[][s] = \prob[\Dom{s}][s] = \prob[V][s] = \prob[v_1, v_2][s] = \prob[][v_1 \mapsto s_1\br{v_1}, v_2 \mapsto s_2\br{v_2}] = \prob[][v_1 \mapsto 2, v_2 \mapsto 1] = \prob[v_1v_2][21] \]
        Each of which should be read as ``the probability that $v_1$ got outcome $2$ and $v_2$ got outcome $1$''
    \end{example}
    \begin{definition}
    \label{def:section_restriction}
    For every $W \subseteq V$ and $s \in \Sect{V}$, the \term{restriction of $s$ onto $W$} (denoted $s|_{W} \in \Sect{W}$) is the section in $\Sect{W}$ that \textit{agrees} with each of $s$'s assignments for variables in $W$.
    \[ \forall v \in W : s|_{W}\br{v} = s\br{v} \]
    \end{definition}
    \begin{definition}
    \label{def:section_compatible}
    The sections $s_{V} \in \Sect{V}$ and $s_{W} \in \Sect{W}$ are said to be \term{compatible} sections if they agree on their valuations of $V \cap W$. Compatibility will be denoted with the infix `$\com$'.
    \[ s_{V} \com s_{W} \iff {s_{V}}|_{V\cap W} = {s_{W}}|_{V\cap W} \]
    \end{definition}
    \begin{definition}
    \label{def:section_extendable}
    It $s_V \in \Sect{V}$ and $s_W \in \Sect{W}$ compatible sections and $W \subseteq V$ then $s_W$ is said to be \term{extendable} to $s_V$. Extendability will be denoted with the infix `$\ext$'.
    \[ s_W \ext s_V \iff s_W \com s_V, W \subseteq V \]
    Extendability is dual to the notion of a \term{restriction} of $s_V$; $s_V$ can be restricted to $s_W$ ($s_V \res s_W$) if and only if $s_W$ is extendable to $s_V$.
    \end{definition}

    \begin{remark}
        The notation `$s \com t$' is used to indicate compatibility between $s \in \Sect{V}$ and $t \in \Sect{W}$ because of the following observation: $s$ and $t$ are compatible if and only if they are extensions of some outcome $r \in \Sect{V \cap W}$.
        \[ s \com t \iff \exists r \in \Sect{V \cap W} \mid s \res r \ext t \]
        In fact $r$ is uniquely defined.
        \[ \forall v \in V \cap W : r\br{v} = s\br{v} = t\br{v} \]
    \end{remark}

    \begin{definition}
        \label{def:extendable_set}
        The set of all extendable sections of $s \in \Sect{W}$ into $V$ is called the \term{extendable set of $s$ into $V$}.
        \[ \Ext[V]{s} \defined \bc{g \in \Sect{V} \mid s \ext g} \subseteq \Sect{V} \]
        The extendable set of $s$ into $V$ is the subset of sections in $\Sect{V}$ that \textit{agrees} with $s$ about valuations for variables in $W$.
    \end{definition}

    \begin{example}
        Let $W = \bc{a, b}$ and $V = \bc{a, b, c}$ be two sets of random variables. Clearly $W \subseteq V$; a prerequisite for extendability. Further impose that the outcome labels for each variable are the same: $O_a = O_b = O_c = \bc{0,1,2}$. As an example, let $s = \bc{a \mapsto s\br{a} = 1, b \mapsto s\br{b} = 2} \in \Sect{W}$. The extendable set of $s$ into $V$ is,
        \[ \Ext[V]{s} = \Ext[a,b,c]{a \mapsto 1, b \mapsto 2} = \bc{\bc{a \mapsto 1, b \mapsto 2, c \mapsto 0}, \bc{a \mapsto 1, b \mapsto 2, c \mapsto 1}, \bc{a \mapsto 1, b \mapsto 2, c \mapsto 2}} \]
    \end{example}

    For every marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$, it is useful to put special emphasis on the \term{joint sections} $\Sect{\jointvar}$. Similarly we define the \term{context sections} $\bc{\Sect{V} \mid V \in \mscenario}$. Finally, we elect to define the disjoint union of all context sections are called the \term{marginal sections} and by an abuse of notation we will denote this disjoint union as $\Sect{\mscenario}$.
    \[ \Sect{\mscenario} = \coprod_{V \in \mscenario} \Sect{V} \]
    Each marginal section $m \in \Sect{\mscenario}$ has a domain $\Dom{m} = V$ for some $V \in \mscenario$.
    \subsubsection{Linear Programs}
    \label{sec:linear_programs}

    We are now fully equipped to write the marginal problem as a matrix multiplication.
    \begin{definition}
        \label{def:incidence_matrix}
        The \term{incidence matrix} $M$ for a marginal scenario $\mscenario = \bc{V_1, \dots, V_k}$ is a bit-wise matrix where the columns are indexed by \textit{joint} sections $j \in \Sect{\jointvar}$ and the rows are indexed by \textit{marginal} sections $m \in \Sect{\mscenario}$. The entries of $M$ are populated whenever a row index is extendable to a column index.
        \[ M_{m,j} = \de_{m \ext j} \defined \begin{cases}
            1 & m \ext j \\
            0 & \text{otherwise}
        \end{cases} \]
        Where $\de_{m \ext j}$ is termed the \term{extendability indicator}. The incidence matrix has $\abs{\Sect{\jointvar}}$ columns, $\abs{\Sect{\mscenario}} = \sum_{i} \abs{\Sect{V_i}}$ rows and $k\abs{\Sect{\jointvar}}$ non-zero entries.
    \end{definition}
    To illustrate this concretely, consider the following example:
    \begin{example}
        \label{ex:incidence_matrix}
        Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{a,b,c}$ and $\mscenario$ be the marginal scenario $\mscenario = \bc{\bc{a,b}, \bc{b,c}, \bc{a,c}}$. The incidence matrix becomes:
        \[ M = \kbordermatrix{
            (a,b,c) \:\: \mapsto & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
            (a\mapsto0, b\mapsto0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
            (a\mapsto0, b\mapsto1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
            (a\mapsto1, b\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
            (a\mapsto1, b\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
            (b\mapsto0, c\mapsto0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
            (b\mapsto0, c\mapsto1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
            (b\mapsto1, c\mapsto0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
            (b\mapsto1, c\mapsto1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
            (a\mapsto0, c\mapsto0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
            (a\mapsto0, c\mapsto1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
            (a\mapsto1, c\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
            (a\mapsto1, c\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
        } \eq \label{eq:example_incidence}\]
    \end{example}

    \begin{definition}
        The \term{joint distribution vector} $\probvec^{\jointvar}$ for a probability distribution $\prob[\jointvar]$ is the vector whose entries are the positive, real-valued probabilities that $\prob[\jointvar]$ assigns to each joint section $j \in \Sect{\jointvar}$. $\probvec^{\jointvar}$ shares the same indices as the \textit{column} indices of $M$.
        \[ \forall j \in \Sect{\jointvar} : \probvec^{\jointvar}_j = \prob[\jointvar][j] \]
    \end{definition}
    \begin{definition}
        The \term{marginal distribution vector} $\probvec^{\mscenario}$ for a marginal model $\prob^{\mscenario} = \bc{P_{V_1}, \ldots, P_{V_k}}$ is the vector whose entries are probabilities over the set of marginal outcomes $\Sect{\mscenario}$. $\probvec^{\mscenario}$ shares the same indices as the \textit{row} indices of $M$.
        \[ \forall m \in \Sect{\mscenario} : \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \]
    \end{definition}
    The marginal and joint distribution vectors are related via the incidence matrix $M$. Given a joint distribution vector $\probvec^{\jointvar}$ one can obtain the marginal distribution vector $\probvec^{\mscenario}$ by multiplying $M$ by $\probvec^{\jointvar}$.
    \[ \probvec^{\mscenario} = M \cdot \probvec^{\jointvar} \eq \label{eq:incidence_matrix_use} \]
    Henceforth we will use $\probvec^{\jointvar}$ ($\probvec^{\mscenario}$) and $\prob[\jointvar]$ ($\prob^{\jointvar}$) interchangeably.

@@

    % \begin{example}
    %     The marginal problem for the inflated causal structure $\ts'$ depicted in \cref{fig:inflated_triangle_scenario} concerns itself with the pre-injectable marginal scenario $\mscenario = \PreInj[\ts]{\ts'} = \bc{V_1, \ldots, V_{12}}$. Equipping the observed nodes of $\ts'$ with $4$-element outcome labels, the incidence matrix $M$ has $16,896$ rows and $16,777,216$ columns.
    %     \begin{align*}
    %         &\text{\# Rows} = \abs{\Sect{\mscenario}} = \sum_{i=1}^{12} \abs{\Sect{V_i}} = \sum_{i=1}^{12} 4^{\abs{V_i}} = 4 \cdot 4^6 + 8 \cdot 4^3 = 16,896 \\
    %         &\text{\# Columns} = \abs{\Sect{\jointvar}} = 4^{\abs{\jointvar}} = 4^{12} = 16,777,216
    %     \end{align*}
    %     With $12 \cdot 4^{12} = 201,326,592$ non-zero entries. For obvious reasons, no attempt is made to reproduce it here.
    % \end{example}
    \begin{definition}
        \label{def:marginal_linear_program}
        \term{The Marginal Linear Program} is the following linear program:
        \begin{alignat*}{2}
            & \text{minimize:} \quad&& \emptyset \cdot x\\
            & \text{subject to:} && x \succeq 0 \\
            & && M \cdot x = \probvec^{\mscenario}
        \end{alignat*}
        If this ``optimization''\footnote{``Optimization'' is presented in quotes here because the minimization objective is trivially always zero ($\emptyset$ denotes the null vector of all zero entries). The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.} is \textit{feasible}, then there exists a vector $x$ than can satisfy \cref{eq:incidence_matrix_use} and is a valid joint distribution vector. Therefore feasibility implies that $\probvec^{\jointvar} = x$. Moreover if the marginal linear program is \textit{infeasible}, then there \textit{does not} exist a joint distribution $\probvec^{\jointvar}$ over all random variables.
    \end{definition}
    \todo[TC]{Talk about about the linear solvers and how this is easy to implement.}
    \begin{definition}
        \label{def:dual_marginal_linear_program}
        \term{The Dual Marginal Linear Program} is the dual of \cref{def:marginal_linear_program} formulated via a procedure similar to~\cite{Lahaie_2008}:
        \begin{alignat*}{2}
            & \text{minimize:} \quad&& y \cdot \probvec^{\mscenario}\\
            & \text{subject to:} && y \cdot M \succeq 0
        \end{alignat*}
        Where $y$ is a real valued vector with the same length as $\probvec^{\mscenario}$.
    \end{definition}

>>>>

% === To allow for labeling of rows and columns of a matrix ===
%\usepackage{kbordermatrix}
\usepackage{../packages/kbordermatrix}
\renewcommand{\kbldelim}{(} % Left delimiter
\renewcommand{\kbrdelim}{)} % Right delimiter

% === Commonly re-occurring symbols ===
\newcommand{\hgraph}{\mathcal{H}}
\newcommand{\graph}{\mathcal{G}}
\newcommand{\nodes}{\mathcal{N}}
\newcommand{\weights}{\mathcal{W}}
\newcommand{\edges}{\mathcal{E}}
\newcommand{\trans}{\mathcal{T}}
\newcommand{\ind}{S}
\newcommand{\inhibit}{\mathcal{I}}
\newcommand{\netperm}{\Pi}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ancestralindep}{\perp}
\newcommand{\valprod}{\times}
\newcommand{\bigvalprod}{\prod}
\newcommand{\com}{\mathrel{\Yright\hspace{-0.2em}\Yleft}}
\newcommand{\ext}{\mathrel{\Yleft}}
\newcommand{\res}{\mathrel{\Yright}}
\newcommand{\gep}{\varphi}
\newcommand{\gp}{\Phi}
\newcommand{\geo}{\omega}
\newcommand{\go}{\Omega}
\newcommand{\mscenario}{\mathcal{M}}
\newcommand{\jointvar}{\mathcal{J}}
% \newcommand{\mset}{\gamma}
% \newcommand{\extmset}{\Gamma}
\newcommand{\supp}[1]{\si\br{#1}}
\newcommand{\kone}{\mathbf{1}}
\newcommand{\kzer}{\textcolor{gray}{0}}

% \newcommand{\mext}[1]{E_{#1}}
% \newcommand{\mul}[1]{\Gamma_{#1}}
\newcommand{\isext}[2]{\delta_{#1 \ext #2}}
\newcommand{\ts}{{\graph}}
% When I introduce a new term or definition
\newcommand{\term}[1]{\textcolor{Mahogany}{\textbf{#1}}}
\newcommand{\tcdot}{} % Tentative cdot, not sure if I want to keep dots

@@

\setoperator{Pa} % Parents of a node
\setoperator{Ch} % Children of a node
\setoperator{An} % Ancestry of a node
\setoperator{Sub} % subgraph
\setoperator{AnSub} % Ancestral subgraph
\setoperator{Ext} % Extension of outcomes
\setoperator{Com} % Compatible equivalence relation
\setoperator{Nec} % Necessary nodes
\setoperator{UnNec} % Unnecessary nodes
\setoperator{Inj} % injectable sets
\setoperator{ImInj} % images of the injectable sets
\setoperator{PreInj} % Pre-injectable sets
\setoperator{ImPreInj} % images of the Pre-injectable sets
\setoperator{Aut} % graph automorphism
\setoperator{Orb} % Group Orbits
\setoperator{Perm} % Permutation group
\newcommand{\PermM}[1]{\La_{#1}} % Permutation matrix
% \setoperator{Out} % Outcome space
\newcommand{\Events}[1]{\s{E}\br{#1}} % Set of events
\newcommand{\Dom}[1]{\s{D}\br{#1}} % Domian
% \setoperator{Dom} % Domian
% \setoperator{Dom} % Domian

@@

    \subsubsection{Events}
    To every discrete random variable $v$ there corresponds a prescribed set of \term{outcomes} $O_v$. We also define the set of all \term{events over $v$} $\Events{v}$\footnote{In the language of sheaf-theory, $\Events{v}$ is the \textit{sheaf of events}~\cite{Abramsky_2011}.} to be the set of all functions $s : \bc{v} \to O_v$ each representing the event that a measurement on $v$ was made where $s\br{v} \in O_v$ was observed.
    \[ \Events{v} \defined \bc{s : \bc{v} \to O_v} \label{eq:outcome_space} \]
    Evidently, $\Events{v}$ and $O_v$ have a one-to-one correspondence and this distinction can be confounding. There is rarely any harm in referring synonymously to either as outcomes. Nonetheless, a sheaf-theoretic treatment of contextuality~\cite{Abramsky_2011} demands the distinction.
    Specifically for this work, the distinction becomes essential for our discussion and exploit of marginal symmetries in \cref{sec:symmetry}. As a natural generalization we define the event over a collection of random variables $V = \bc{v_1, \ldots, v_n}$ in a parallel manner,
    \[ \Events{V} \defined \bc{s: V \to O_{V} \mid \forall i : s\br{v_i} \in O_{v_i} } \eq \label{eq:outcome_space}\]
    Each event $s$ can be compactly represented as a set of mappings over each element of $V$.
    \[ s = \bc{v_1 \mapsto s\br{v_1}, \ldots, v_k \mapsto s\br{v_k}} = \bc{v_i\mapsto s\br{v_i}}_{i = 1}^{k} \]
    The domain $\Dom{s}$ of an event $s$ is the set of random variables it valuates, i.e. if $s \in \Events{V}$, then $\Dom{s} = V$.
    \begin{example}
        Let $s \in \Events{V}$ be an event over $V$, a probability distribution $\prob[V]$ over $V$ will assign a non-negative probability $\prob[V][s]$ to $s$. Let $V = \bc{v_1, v_2}$ with each $v \in V$ having $3$ distinct outcomes $O_v = \bc{0,1,2}$. Furthermore let $f \in \Events{V}$ be the section $\br{v_1 \mapsto 2, v_2 \mapsto 1}$. Then the following notations are interchangeable,
        \[ \prob[][s] = \prob[\Dom{s}][s] = \prob[V][s] = \prob[v_1, v_2][s] = \prob[][v_1 \mapsto s_1\br{v_1}, v_2 \mapsto s_2\br{v_2}] = \prob[][v_1 \mapsto 2, v_2 \mapsto 1] = \prob[v_1v_2][21] \]
        Each of which should be read as ``the probability that $v_1$ got outcome $2$ and $v_2$ got outcome $1$''
    \end{example}
    \begin{definition}
    \label{def:section_restriction}
    For every $W \subseteq V$ and $s \in \Events{V}$, the \term{restriction of $s$ onto $W$} (denoted $s|_{W} \in \Events{W}$) is the event in $\Events{W}$ that \textit{agrees} with each of $s$'s assignments for variables in $W$.
    \[ \forall v \in W : s|_{W}\br{v} = s\br{v} \]
    \end{definition}
    \begin{definition}
    \label{def:section_compatible}
    The events $s_{V} \in \Events{V}$ and $s_{W} \in \Events{W}$ are said to be \term{compatible} events if they agree on their valuations of $V \cap W$. Compatibility will be denoted with the infix `$\com$'.
    \[ s_{V} \com s_{W} \iff {s_{V}}|_{V\cap W} = {s_{W}}|_{V\cap W} \]
    \end{definition}
    \begin{definition}
    \label{def:section_extendable}
    It $s_V \in \Events{V}$ and $s_W \in \Events{W}$ compatible events and $W \subseteq V$ then $s_W$ is said to be \term{extendable} to $s_V$. Extendability will be denoted with the infix `$\ext$'.
    \[ s_W \ext s_V \iff s_W \com s_V, W \subseteq V \]
    Extendability is dual to the notion of a \term{restriction} of $s_V$; $s_V$ can be restricted to $s_W$ ($s_V \res s_W$) if and only if $s_W$ is extendable to $s_V$.
    \end{definition}

    \begin{remark}
        The notation `$s \com t$' is used to indicate compatibility between $s \in \Events{V}$ and $t \in \Events{W}$ because of the following observation: $s$ and $t$ are compatible if and only if they are extensions of some event $r \in \Events{V \cap W}$.
        \[ s \com t \iff \exists r \in \Events{V \cap W} \mid s \res r \ext t \]
        In fact $r$ is uniquely defined.
        \[ \forall v \in V \cap W : r\br{v} = s\br{v} = t\br{v} \]
    \end{remark}

    For every marginal scenario $\mscenario = \bc{V_1, \ldots, V_k}$, it is useful to put special emphasis on the \term{joint events} $\Events{\jointvar}$. Similarly we define the \term{context events} $\bc{\Events{V} \mid V \in \mscenario}$. Finally, we elect to define the disjoint union of all context events are called the \term{marginal events} and by an abuse of notation we will denote this disjoint union as $\Events{\mscenario}$.
    \[ \Events{\mscenario} = \coprod_{V \in \mscenario} \Events{V} \]
    Each marginal section $m \in \Events{\mscenario}$ has a domain $\Dom{m} = V$ for some $V \in \mscenario$.
    \subsubsection{Linear Programs}
    \label{sec:linear_programs}

    We are now fully equipped to write the marginal problem as a matrix multiplication.
    \begin{definition}
        \label{def:incidence_matrix}
        The \term{incidence matrix} $M$ for a marginal scenario $\mscenario = \bc{V_1, \dots, V_k}$ is a bit-wise matrix where the columns are indexed by \textit{joint} events $j \in \Events{\jointvar}$ and the rows are events by \textit{marginal} sections $m \in \Events{\mscenario}$. The entries of $M$ are populated whenever a row index is extendable to a column index.
        \[ M_{m,j} = \de_{m \ext j} \defined \begin{cases}
            1 & m \ext j \\
            0 & \text{otherwise}
        \end{cases} \]
        Where $\de_{m \ext j}$ is termed the \term{extendability indicator}. The incidence matrix has $\abs{\Events{\jointvar}}$ columns, $\abs{\Events{\mscenario}} = \sum_{i} \abs{\Events{V_i}}$ rows and $k\abs{\Events{\jointvar}}$ non-zero entries.
    \end{definition}
    To illustrate this concretely, consider the following example:
    \begin{example}
        \label{ex:incidence_matrix}
        Let $\jointvar$ be $3$ binary variables $\jointvar = \bc{a,b,c}$ and $\mscenario$ be the marginal scenario $\mscenario = \bc{\bc{a,b}, \bc{b,c}, \bc{a,c}}$. The incidence matrix becomes:
        \[ M = \kbordermatrix{
            (a,b,c) \:\: \mapsto & (0,0,0) & (0,0,1) & (0,1,0) & (0,1,1) & (1,0,0) & (1,0,1) & (1,1,0) & (1,1,1) \\
            (a\mapsto0, b\mapsto0) & \kone & \kone & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer \\
            (a\mapsto0, b\mapsto1) & \kzer & \kzer & \kone & \kone & \kzer & \kzer & \kzer & \kzer \\
            (a\mapsto1, b\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kone & \kzer & \kzer \\
            (a\mapsto1, b\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kone \\
            (b\mapsto0, c\mapsto0) & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer \\
            (b\mapsto0, c\mapsto1) & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer & \kzer \\
            (b\mapsto1, c\mapsto0) & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone & \kzer \\
            (b\mapsto1, c\mapsto1) & \kzer & \kzer & \kzer & \kone & \kzer & \kzer & \kzer & \kone \\
            (a\mapsto0, c\mapsto0) & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer & \kzer \\
            (a\mapsto0, c\mapsto1) & \kzer & \kone & \kzer & \kone & \kzer & \kzer & \kzer & \kzer \\
            (a\mapsto1, c\mapsto0) & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone & \kzer \\
            (a\mapsto1, c\mapsto1) & \kzer & \kzer & \kzer & \kzer & \kzer & \kone & \kzer & \kone
        } \eq \label{eq:example_incidence}\]
    \end{example}

    \begin{definition}
        The \term{joint distribution vector} $\probvec^{\jointvar}$ for a probability distribution $\prob[\jointvar]$ is the vector whose entries are the positive, real-valued probabilities that $\prob[\jointvar]$ assigns to each joint event $j \in \Events{\jointvar}$. $\probvec^{\jointvar}$ shares the same indices as the \textit{column} indices of $M$.
        \[ \forall j \in \Events{\jointvar} : \probvec^{\jointvar}_j = \prob[\jointvar][j] \]
    \end{definition}
    \begin{definition}
        Analogously, \term{marginal distribution vector} $\probvec^{\mscenario}$ for a marginal model $\prob^{\mscenario} = \bc{P_{V_1}, \ldots, P_{V_k}}$ is the vector whose entries are probabilities over the set of marginal outcomes $\Events{\mscenario}$. $\probvec^{\mscenario}$ shares the same indices as the \textit{row} indices of $M$.
        \[ \forall m \in \Events{\mscenario} : \probvec^{\mscenario}_m = \prob[\Dom{m}][m] \]
    \end{definition}
    The marginal and joint distribution vectors are related via the incidence matrix $M$. Given a joint distribution vector $\probvec^{\jointvar}$ one can obtain the marginal distribution vector $\probvec^{\mscenario}$ by multiplying $M$ by $\probvec^{\jointvar}$.
    \[ \probvec^{\mscenario} = M \tcdot \probvec^{\jointvar} \eq \label{eq:incidence_matrix_use} \]
    Henceforth we will use $\probvec^{\jointvar}$ ($\probvec^{\mscenario}$) and $\prob[\jointvar]$ ($\prob_{\mscenario}$) interchangeably.

@@

    \begin{definition}
        \label{def:marginal_linear_program}
        \term{The Marginal Linear Program} is the following linear program:
        \begin{alignat*}{2}
            & \text{minimize:} \quad&& \emptyset \tcdot x\\
            & \text{subject to:} && x \succeq 0 \\
            & && M \tcdot x = \probvec^{\mscenario}
        \end{alignat*}
        If this ``optimization''\footnote{``Optimization'' is presented in quotes here because the minimization objective is trivially always zero ($\emptyset$ denotes the null vector of all zero entries). The primal value of the linear program is of no interest, all that matters is its \textit{feasibility}.} is \textit{feasible}, then there exists a vector $x$ than can satisfy \cref{eq:incidence_matrix_use} and is a valid joint distribution vector. Therefore feasibility implies that $\probvec^{\jointvar} = x$. Moreover if the marginal linear program is \textit{infeasible}, then there \textit{does not} exist a joint distribution $\probvec^{\jointvar}$ over all random variables.
    \end{definition}
    \todo[TC]{Talk about about the linear solvers and how this is easy to implement.}
    \begin{definition}
        \label{def:dual_marginal_linear_program}
        \term{The Dual Marginal Linear Program} is the dual of \cref{def:marginal_linear_program} formulated via a procedure similar to~\cite{Lahaie_2008}:
        \begin{alignat*}{2}
            & \text{minimize:} \quad&& y \tcdot \probvec^{\mscenario}\\
            & \text{subject to:} && y \tcdot M \succeq 0
        \end{alignat*}
        Where $y$ is a real valued vector with the same length as $\probvec^{\mscenario}$.
    \end{definition}

    The dual marginal linear program not only answers the marginal problem for a specific marginal model $\probvec^{\mscenario}$ but as a by-product provides an inequality that witnesses its contextuality. If this is not obvious, first notice that the dual problem is \textit{never infeasible}; by choosing $y$ to be trivially the null vector $\emptyset$ of appropriate size, all constraints become satisfied. Secondly if the dual constraint $y \tcdot M \succeq 0$ holds \textit{and} the primal is feasible, then the following must hold:
    \[ y \tcdot \probvec^{\mscenario} =  y \tcdot M \tcdot x \geq 0 \eq \label{eq:dual_marginal_ineq} \]
    Therefore the \textit{sign} of the dual value $d \defined \min \br{y \tcdot \probvec^{\mscenario}}$ classifies a marginal model's contextuality. If $d < 0$ then \cref{eq:dual_marginal_ineq} is violated and therefore $\probvec^{\mscenario}$ is contextual. Likewise if $d \geq 0$ (satisfying \cref{eq:dual_marginal_ineq}), then $\probvec^{\mscenario}$ is non-contextual. \footnote{Actually, if $d \geq 0$ then it is exactly $d = 0$ due to the existence of the trivial $y = \emptyset$. This observation is an instance of the \textit{Complementary Slackness Property} of~\cite{Bradley_1977}. \comment[TC]{Is this really the CSP?} Moreover, if $d < 0$, then it is unbounded $d = -\inf$. This latter point becomes clear upon recognizing that for any $y$ with $d < 0$, another $y' = \al y$ can be constructed (with $\al > 1$) such that $d' = \al d < d$. Since a more negative $d'$ can always be found, it must be that $d$ is unbounded. This is a demonstration of the fundamental \textit{Unboundedness Property} of~\cite{Bradley_1977}; if the dual is unbounded, then the primal is infeasible. \comment[TC]{\href{http://web.stanford.edu/~ashishg/msande111/notes/chapter4.pdf}{Farkas's lemma} here?}}

    \begin{definition} An \term{infeasibility certificate}~\cite{Andersen_2001} is any vector $y$ that satisfies the constraint of \cref{def:dual_marginal_linear_program} and also permits violation of \cref{eq:dual_marginal_ineq} for some marginal distribution vector $\probvec^{\mscenario}$.
    \[ y \in \R^{\abs{\Events{\mscenario}}} : y \tcdot M \succeq 0, \quad y \tcdot \probvec^{\mscenario} < 0 \]
    Furthermore, for every $y$ satisfying $y \tcdot M \succeq 0$ there corresponds a \term{certificate inequality} that constraints the set of non-contextual marginal models $\s{NC}$,
    \[ \forall \probvec^{\mscenario} \in \s{NC} : y \tcdot \probvec^{\mscenario} \geq 0 \]
    \end{definition}
